Paper notes

### 2019-08-28 paper_notes.Rmd
ok_values

f_val <- function(e_w,ew_ng,M,i_v,S_v){
  if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
    U <- 1
    }else{
      U <- (M + ((1-(round(abs(e_w-ew_ng), digits=2)))*(1-M))/(1-i_v)) * S_v
      }
  round(U,digits = 3)
  }

@@

$$
U^i_v=
\begin{cases}
1, & \text{if} \ \mid{\overline{ew}_j - ew_i}\mid \leq i_v, \\
\\
\left(M + \frac{(1 - \mid{\overline{ew}_j - ew_i}\mid) \times (1 - M)}{1 - i_v}\right) \times S_v, & otherwise
\end{cases}
$$

@@

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S_v <- 1
M <- 1

fvf0p  <- f_val(e_w,0,M,i_v,S_v)
fvf1p  <- f_val(e_w,0.1,M,i_v,S_v)
fvf2p   <- f_val(e_w,0.2,M,i_v,S_v)
fvf3p   <- f_val(e_w,0.3,M,i_v,S_v)
fvf4p   <- f_val(e_w,0.4,M,i_v,S_v)
fvf5p   <- f_val(e_w,0.5,M,i_v,S_v)
fvf6p   <- f_val(e_w,0.6,M,i_v,S_v)
fvf7p   <- f_val(e_w,0.7,M,i_v,S_v)
fvf8p   <- f_val(e_w,0.8,M,i_v,S_v)
fvf9p  <- f_val(e_w,0.9,M,i_v,S_v)
fvf10p  <- f_val(e_w,1.0,M,i_v,S_v)

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S_v <- 0
M <- 0

fvf0t <- f_val(e_w,0,M,i_v,S_v)
fvf1t  <- f_val(e_w,0.1,M,i_v,S_v)
fvf2t   <- f_val(e_w,0.2,M,i_v,S_v)
fvf3t   <- f_val(e_w,0.3,M,i_v,S_v)
fvf4t   <- f_val(e_w,0.4,M,i_v,S_v)
fvf5t   <- f_val(e_w,0.5,M,i_v,S_v)
fvf6t  <- f_val(e_w,0.6,M,i_v,S_v)
fvf7t   <- f_val(e_w,0.7,M,i_v,S_v)
fvf8t   <- f_val(e_w,0.8,M,i_v,S_v)
fvf9t  <- f_val(e_w,0.9,M,i_v,S_v)
fvf10t  <- f_val(e_w,1.0,M,i_v,S_v)

@@

symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Symmetric Single Peaked (S=1,M=0) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))

>>>>

f_val <- function(e_w,ew_ng,i_v,S_v){
  if (round(abs(e_w-ew_ng), digits=2) <= i_v) {
    U <- 1
    }else{
      U <- ((1-(round(abs(e_w-ew_ng), digits=2)))/(1-i_v)) * S_v
      }
  round(U,digits = 3)
  }

@@

$$
U^i_v=
\begin{cases}
1, & \text{if} \ \mid{\overline{ew}_j - ew_i}\mid \leq i_v, \\
\\
\left(\frac{(1 - \mid{\overline{ew}_j - ew_i}\mid) }{1 - i_v}\right) \times S_v, & otherwise
\end{cases}
$$

@@

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S_v <- 1

fvf0p  <- f_val(e_w,0,i_v,S_v)
fvf1p  <- f_val(e_w,0.1,i_v,S_v)
fvf2p   <- f_val(e_w,0.2,i_v,S_v)
fvf3p   <- f_val(e_w,0.3,i_v,S_v)
fvf4p   <- f_val(e_w,0.4,i_v,S_v)
fvf5p   <- f_val(e_w,0.5,i_v,S_v)
fvf6p   <- f_val(e_w,0.6,i_v,S_v)
fvf7p   <- f_val(e_w,0.7,i_v,S_v)
fvf8p   <- f_val(e_w,0.8,i_v,S_v)
fvf9p  <- f_val(e_w,0.9,i_v,S_v)
fvf10p  <- f_val(e_w,1.0,i_v,S_v)

e_w <- 0.2
e_w_ng <- seq(0.0,1.0, by = 0.1)
i_v <- 0.1
S_v <- 0

fvf0t <- f_val(e_w,0,i_v,S_v)
fvf1t  <- f_val(e_w,0.1,i_v,S_v)
fvf2t   <- f_val(e_w,0.2,i_v,S_v)
fvf3t   <- f_val(e_w,0.3,i_v,S_v)
fvf4t   <- f_val(e_w,0.4,i_v,S_v)
fvf5t   <- f_val(e_w,0.5,i_v,S_v)
fvf6t  <- f_val(e_w,0.6,i_v,S_v)
fvf7t   <- f_val(e_w,0.7,i_v,S_v)
fvf8t   <- f_val(e_w,0.8,i_v,S_v)
fvf9t  <- f_val(e_w,0.9,i_v,S_v)
fvf10t  <- f_val(e_w,1.0,i_v,S_v)

@@

symm_val_plot <- symm_val_graph + geom_point() + theme_bw() + labs(x = "Mean ethnic weight neighborhood j",y = "Value utility j") + ggtitle(label = "Symmetric Single Peaked (S=1) ",subtitle = subt_cont_v) + theme(plot.title = element_text(hjust = 0.5), plot.subtitle = element_text(hjust = 0.5))  + scale_x_continuous(breaks = seq(0.0,1.0,by = 0.1)) + scale_y_continuous(limits =  c(0.0,1.0), breaks = seq(0.0,1.0,by = 0.25))
